Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-05-04 doc/RMD/mlg-mcg.Rmd
fix group colors

the_communities <- data_frame(vertex = lay2$name, community = lay2$community) %>%
  group_by(community) %>%
  mutate(comm = ifelse(n() > 10, paste("Community", community), "Other Communities (n < 10)")) %>%
  mutate(comm = forcats::fct_infreq(comm) %>% forcats::fct_shift(-1L))
lay2$community <- the_communities$comm

mcg_mlg_graph <- ggraph(lay2) +
  geom_node_circle(aes(r = size, lty = type, fill = community)) +
  geom_edge_link(aes(start_cap = circle(node1.size, unit = "native"), 
                     end_cap = circle(node2.size, unit = "native"), 
                     width = weight),
                 arrow = arrow(length = unit(0.01, "native"))) +
  geom_node_text(aes(label = gsub("MLG.", "", name), 
                     color = ifelse(grepl("ther", community), "A", ifelse(grepl("3", community), "B", "C")), 
                     size = size/10), 
                 show.legend = FALSE) +
  coord_fixed() +
  scale_edge_width(range = c(0.25, 1.5)) +
  scale_color_manual(values = c("white", "grey75", "black")) +
  scale_fill_viridis(direction = -1, discrete = TRUE) +
  theme_graph(base_size = 16, base_family = "Helvetica") +
  theme(legend.position = "bottom", legend.direction = "vertical") +
  ggtitle("Relation of Multilocus Genotypes and MCGs")

@@

```{r top5graph, fig.height = 7, fig.width = 7}
top5 <- filter(mcgmlg, as.character(MCG) %in% mcgs$MCG[1:5])
top5g <- make_mcgmlg_graph(top5) %>% add_communities(cluster_walktrap(g))
tosize <- V(top5g)$size
V(top5g)$size <- sqrt(tosize)/10
set.seed(2017-05-04)
top5lay <- create_layout(top5g, layout = "igraph", algorithm = "nicely")
top5lay$community <- inner_join(data_frame(vertex = top5lay$name), the_communities)$comm
t5g <- mcg_mlg_graph %+% top5lay + ggtitle("Top 5 Mycelial Compatibility Groups and associated MLGs")
t5g
ggsave(t5g, file = file.path("results", "figures", "publication", "FigureS2B.svg"), width = 88, height = 88, scale = 3, units = "mm")
```

>>>>

cnames <- LETTERS[1:10]
cnames[c(7, 5, 1)] <- LETTERS[1:3]
the_communities <- data_frame(vertex = lay2$name, community = lay2$community) %>%
  mutate(community = case_when(
    .$community == 7 ~ "A",
    .$community == 5 ~ "B",
    .$community == 1 ~ "C",
    TRUE ~ as.character(.$community)
  )) %>%
  group_by(community) %>%
  mutate(comm = ifelse(n() > 10, paste("Community", community), "Other Communities (n < 10)")) %>%
  mutate(comm = comm) # It just so happens that the communities are in order by size.
lay2$community <- the_communities$comm
mcg_mlg_graph <- ggraph(lay2) +
  geom_node_circle(aes(r = size, lty = type, fill = community)) +
  geom_edge_link(aes(start_cap = circle(node1.size, unit = "native"), 
                     end_cap = circle(node2.size, unit = "native"), 
                     width = weight),
                 arrow = arrow(length = unit(0.01, "native"))) +
  geom_node_text(aes(label = gsub("MLG.", "", name), 
                     color = community, 
                     size = size/10), 
                 show.legend = FALSE) +
  coord_fixed() +
  scale_linetype_manual(values = c(1, 3)) +
  scale_edge_width(range = c(0.25, 1.5)) +
  scale_color_manual(values = c("black", "black", "white", "white")) +
  scale_fill_viridis(direction = -1, discrete = TRUE) +
  theme_graph(base_size = 16, base_family = "Helvetica") +
  theme(legend.position = "bottom", legend.direction = "vertical") +
  ggtitle("Relation of Multilocus Genotypes and MCGs")

@@

```{r top5graph, fig.height = 7, fig.width = 7}
top5 <- filter(mcgmlg, as.character(MCG) %in% mcgs$MCG[1:5])
top5g <- make_mcgmlg_graph(top5)
tosize <- V(top5g)$size
V(top5g)$size <- sqrt(tosize)/10
set.seed(2017-05-04)
top5lay <- create_layout(top5g, layout = "igraph", algorithm = "nicely")
top5lay$community <- inner_join(data_frame(vertex = top5lay$name), the_communities)$comm
t5g <- mcg_mlg_graph %+% top5lay + ggtitle("Top 5 Mycelial Compatibility Groups and associated MLGs")
t5g
ggsave(t5g, file = file.path("results", "figures", "publication", "FigureS2B.svg"), width = 88, height = 88, scale = 3, units = "mm")
```
